Single-fluorophore orientation determination with multiview polarized illumination: modeling and microscope design

### 2017-08-13 paper/paper/paper.tex
Hari's second round of edits.

Recently, there has been increasing interest in multiview microscopy techniques
for biological imaging \cite{wu2013, keller2015, wu2016, wu2017}. Multiview
microscopes offer two major advantages over single-view microscopes. First,
multiview microscopes can achieve nearly isotropic resolution compared to the
anisotropic resolution of single-view microscopes whose axial resolution is
reduced by at least a factor of two compared to lateral resolution. Second,
multiview microscopes can use light-sheet illumination to reduce phototoxicity
without requiring a dedicated illumination path. For example, if two orthogonal
objectives are focused on the same point, then the objectives can alternate
roles as the light-sheet illumination path and as the detection
path. Light-sheet illumination offers a major reduction of phototoxicity because
a light sheet only illuminates in-focus regions while other widefield and
confocal approaches inevitably illuminate out-of-focus regions. Together, these
advantages make multiview microscopes good candidates for imaging live
biological specimens for long periods.

@@

\subsection{Intensity Measurements}\label{forward}
The detected intensity is the product of the the sample exposure
$I_{\text{tot}}$, the absorption efficiency, and the detection efficiency
\begin{align}
  I = I_{\text{tot}}\eta_{\text{abs}}\eta_{\text{det}}\label{eq:forward_frame}.
\end{align}
Equation \ref{eq:forward_frame} is the forward model for a single intensity
measurement. Figure \ref{fig:single-frame} shows the efficiencies in three
representative geometries. Note that in all cases there are multiple
orientations that give the same intensity measurement. This means that a single
intensity measurement does not give us enough information to reconstruct the
orientation of a single molecule. Next, we will consider combining several
intensity measurements to create complete polarized illumination microscopes.

@@

To compare microscopes with different numbers of intensity measurements fairly,
we kept the total exposure to the sample constant by choosing
$I_{\text{tot}} = \frac{4000}{N}$. Note that $I_{\text{tot}}$ is a measure of
exposure to the sample, not the detected intensity or the total intensity
emitted by the molecule.

>>>>

Recently, there has been increasing interest in multiview microscopy techniques
for biological imaging \cite{wu2013, keller2015, wu2016, wu2017}. Multiview
microscopes offer two major advantages over single-view microscopes. First,
multiview microscopes can achieve nearly isotropic resolution compared to the
anisotropic resolution of single-view microscopes whose axial resolution is
reduced by at least a factor of two compared to lateral resolution. Second,
multiview microscopes can use light-sheet illumination to reduce phototoxicity
while reusing parts of the optical path for both illumination and detection. For
example, if two orthogonal objectives are focused on the same point, then the
objectives can alternate roles as the light-sheet illumination path and as the
detection path. Light-sheet illumination offers a major reduction of
phototoxicity because a light sheet only illuminates in-focus regions while
other widefield and confocal approaches inevitably illuminate out-of-focus
regions. Together, these advantages make multiview microscopes good candidates
for imaging live biological specimens for long periods.

@@

\subsection{Intensity Measurements}\label{forward}
The detected intensity is the product of the the sample exposure
$I_{\text{exp}}$, the absorption efficiency, and the detection efficiency
\begin{align}
  I = I_{\text{exp}}\eta_{\text{abs}}\eta_{\text{det}}\label{eq:forward_frame}.
\end{align}
Equation \ref{eq:forward_frame} is the forward model for a single intensity
measurement. Figure \ref{fig:single-frame} shows the efficiencies in three
representative geometries. Note that in all cases there are multiple
orientations that give the same intensity measurement. This means that a single
intensity measurement does not give us enough information to reconstruct the
orientation of a single molecule. Next, we will consider combining several
intensity measurements to create complete polarized illumination microscopes.

@@

To compare microscopes with different numbers of intensity measurements fairly,
we kept the total exposure to the sample constant by choosing
$I_{\text{exp}} = \frac{4000}{N}$. Note that $I_{\text{exp}}$ is a measure of
exposure to the sample, not the detected intensity or the total intensity
emitted by the molecule.
